Comparison among doublet predictions on benchmarking datasets

### 2024-07-02 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
plot theming

theme_set(theme_bw())

@@

  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} %in% c("fp", "fn")), 
    size = 0.75
  ) +
  scale_color_manual(name = "Call type", values = metric_colors) +
  ggtitle("Consensus class metrics") +
  guides(color = guide_legend(override.aes = list(size = 2)))

}
```

>>>>

theme_set(
  theme_bw() + 
    theme(
      legend.title = element_text(size = rel(1.1)),
      legend.text = element_text(size = rel(1.1))
  )
)

@@

  ggplot(df) + 
    aes(x = PC1, 
        y = PC2, 
        color = {{color_column}}) +
  geom_point(
    size = 0.75, 
    alpha = 0.6
  ) + 
  geom_point(
    data = dplyr::filter(df, {{color_column}} %in% c("fp", "fn")), 
    size = 0.75
  ) +
  scale_color_manual(name = "Call type", values = metric_colors) +
  ggtitle("Consensus call metrics") +
  guides(color = guide_legend(override.aes = list(size = 2)))
}
```
